---
title: "Dose response assay plots"
author: "Emily J Tallerday"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = T , 
                      warning = F , # including this is the ONLY way to get rid of the warnings in the flowering time plot! doing stuff inside that code chunk itself does NOT work. 
                     # message = F #,
                      # results = "hide" , 
                      error = F #,  
                      # include = F
                      )
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```

# Load general packages & functions

## Packages & set themes

```{r, include = F, echo = F}
packages <- c("rmarkdown","pandoc","formatR","tidyverse","gridExtra","ggpubr","viridis","ggthemes","here","gplots","cowplot","ggtext","ggsignif","ggokabeito")
lapply(packages, require, character.only=T)

```

The packages being used are as follows:

`packages <- c("rmarkdown","pandoc","formatR","tidyverse","gridExtra","ggpubr","viridis","ggthemes","here","gplots","cowplot","ggtext","ggsignif","ggokabeito")`

and can be loaded using:

`lapply(packages, require, character.only=T)`

The ggplot theme used:

```{r}
theme_set(theme_light())
```

# Actual data from Eva

## Import & organize data

```{r}
BA_response <- read.csv(here(r"(Data\06292023_Eva_BA response data.csv)"))
```

### Adjusting things in df to make plotting easier

```{r}
BA_response$treatment[BA_response$treatment == 'veh'] <- 0
BA_response$genotype <- as.factor(BA_response$genotype)
BA_response$treatment <- as.numeric(BA_response$treatment)
colnames(BA_response) <- c("Genotype","Conc. BA (ng/uL)", "Shoot length (cm)", "Root length (cm)")
```

## Plotting

Modified from: <https://rpkgs.datanovia.com/ggpubr/reference/stat_regline_equation.html>

```{r, echo = T, include=T, dev = "png", dpi = 300}
BA_response %>%
ggplot(aes(x = `Conc. BA (ng/uL)`, y = `Root length (cm)`, color = Genotype, fill = Genotype)) +
  geom_point(shape = 21, size = 2, alpha = 0.5, color = "black") +
  geom_smooth(method = "lm", se = T, alpha = 0.2) +
  facet_wrap(~Genotype,
             ncol = 4,
             nrow = 1,
             scales = "free"
             ) +
  theme( strip.background = element_blank() ) +
  
  # stat_cor(#label.y = 8.8, 
  #          #label.x = 10.5, 
  #          color = "black") + 
  stat_regline_equation(#label.y = 8, 
                        #label.x = 10.5, 
                        color = "black") + 
  
  labs(
    color = "Genotype", # in legend
    fill = "Genotype" # in legend
  ) +
  #scale_color_hue(labels = Genotype) + # color variable
  #theme(legend.text = element_markdown()) +
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() %>% # fill variable 
  suppressWarnings() %>%
  suppressMessages()
```

# Session info

```{r, include=T, echo=T}
sessionInfo()
```
